---
title: "QUD Kids"
author: "Hugh Rabagliati"
date: "5 November 2014"
output: html_document
---

Working Directory should be "AdultExperiment".

***Action data***

We read in action data from a single Excel spreadsheet, and then graph it and analyze it.

1) Read in the data
```{r, echo=FALSE}
library(doBy)
library(lme4)

qud.a <- read.csv("./Actions/actions.csv", header = T)
qud.a$Age <- as.factor(ifelse(qud.a$Age.group ==1, "five","seven"))
qud.a <- qud.a[!is.na(qud.a$Instr),]
contrasts(qud.a$Age)[1] <- -1
contrasts(qud.a$QuestCond)[1] <- -1
contrasts(qud.a$VerbCond)[1] <- -1
```

2) Graph the data
```{r}
k <- summaryBy(Instr~QuestCond+VerbCond+Age+Participant.no, data = qud.a, FUN = c(mean,sd))
k <- summaryBy(Instr.mean~QuestCond+VerbCond+Age, data = k, FUN = c(mean,sd))
k$SE = k$Instr.mean.sd/sqrt(6)
k$VerbCond = factor(k$VerbCond, levels(k$VerbCond)[c(2,1)])
tapply(k$Instr.mean.mean, list(k$QuestCond,k$VerbCond,k$Age), FUN = mean) -> o
tapply(k$SE, list(k$QuestCond,k$VerbCond,k$Age), FUN = mean) -> se
old.par <- par(mfrow=c(1, 2))
 barplot(o[,,1], beside =T , ylim = c(-0.1,1.1),col = "white",  border = NA, ylab = "Proportion actions using Instrument",  main = "5-year-olds",names.arg = c("Instrument-bias verb", "Equi-bias verb"))
 legend(1.8,0.5, legend = c("Instrument Question", "Modifier Question"), bty = "n", col = c("black","grey"), pch = 20)
 points(c(1.5,4.5), o[1,,1], pch = 20, cex = 2, col = "black")
 points(c(2.5,5.5), o[2,,1], pch = 20, cex = 2, col = "grey")
 grid(nx = NA, ny = NULL, col = "gray", lty = "dotted",lwd = par("lwd"), equilogs = TRUE)
  arrows(c(1.5,2.5,4.5,5.5), (c(o[,,1]) + c(se[,,1])), c(1.5,2.5,4.5,5.5), (c(o[,,1]) - c(se[,,1])), code = 0)

 barplot(o[,,2], beside =T , ylim = c(-0.1,1.1),col = "white",  border = NA, ylab = "Proportion actions using Instrument",  main = "7-year-olds",names.arg = c("Instrument-bias verb", "Equi-bias verb"))
 points(c(1.5,4.5), o[1,,2], pch = 20, cex = 2, col = "black")
 points(c(2.5,5.5), o[2,,2], pch = 20, cex = 2, col = "grey")
 grid(nx = NA, ny = NULL, col = "gray", lty = "dotted",lwd = par("lwd"), equilogs = TRUE)
 arrows(c(1.5,2.5,4.5,5.5), (c(o[,,2]) + c(se[,,2])), c(1.5,2.5,4.5,5.5), (c(o[,,2]) - c(se[,,2])), code = 0)
 par(old.par)
```

Analyzing this data turned out to be hard, because we have considerable "separation" - where a predictor perfectly separates two groups of data (ie our experiment worked too well!).
We began by trying to use logistic regression, but the separation meant that it wouldnt fit. So, we used ANOVAs, calculating p values by permutation. To avoid this document taking all day to generate, we just use 100 permutations here.

Our ANOVA is 2 (age) * 2(QUD) * 2 (verb bias), and the print out at the end is a standard ANOVA, and then the set of permutation-derived p values.

```{r, echo=FALSE}
#How about an ANOVA using permutation tests to calculate p values?
summaryBy(Instr~Participant.no+VerbCond+QuestCond+Age, data = qud.a, keep.names = T) -> qud.sum
nreps <- 100
Act.ANOVA = matrix(data = NA, nrow = nreps, ncol = 7)
summary(aov(lm(Instr~Age*VerbCond*QuestCond, data = qud.sum))) -> perm.orig
for (j in 1:7){
  Act.ANOVA[1,j] <- perm.orig[[1]]$"F value"[j]
  }
for (i in 2:nreps) {
  newInstr <- sample(qud.sum$Instr, length(qud.sum$Instr))
  mod2 <- lm(newInstr~qud.sum$Age*qud.sum$VerbCond*qud.sum$QuestCond)
  b <- summary(aov(mod2))
  for (j in 1:7){
  Act.ANOVA[i,j] <- b[[1]]$"F value"[j]
  	}
  }
print(perm.orig)
for (i in 1:7){
print(length(Act.ANOVA[,i][Act.ANOVA[,i]>=Act.ANOVA[1,i]])/nreps)
 }


```

*** Eye tracking graphs and analysis***

To process the data for analysis (take in the Excel files, expand them over timepoints), we need to load in the scripts in the proc_subj.r, ET_Import.r and Graphing.r files. Once that's done, we run the first set of code in QUD_Summary, which produces the dataframe QUD_Expand. That can also be loaded up, as below.

```{r}
load("QUD_Expand_Child.RDATA")
```

We'll need to import some libraries for plotting etc. 

```{r, echo=FALSE}
library(reshape2)
library(plyr)
library(car)
require(gdata)
require(ggplot2)
require(longitudinalData)
```

And now construct and then melt the dataframes that we use for plotting

```{r}

se <- function(x){
  x <- sd(x)/sqrt(6)
	return(x)
	}

QUD.Graph <- summaryBy(Inst+TA+DA+DI~TimeFrame+Cond+QCond+Name.+Age, data = QUD.Expand[QUD.Expand$TimeFrame > -300 & QUD.Expand$TimeFrame <=1500,], FUN = c(mean),keep.names = T)
QUD.Graph <- summaryBy(Inst+TA+DA+DI~TimeFrame+Cond+QCond+Age, data = QUD.Graph, FUN = c(mean,se))
levels(QUD.Graph$QCond)[levels(QUD.Graph$QCond)=="Inst"] <- "Instrument Question"
levels(QUD.Graph$QCond)[levels(QUD.Graph$QCond)=="Mod"] <- "Modifier Question"
levels(QUD.Graph$Cond)[levels(QUD.Graph$Cond)=="Inst"] <- "Instrument-bias Verbs"
levels(QUD.Graph$Cond)[levels(QUD.Graph$Cond)=="Equi"] <- "Equi-bias Verbs"
QUD.Graph$Cond <- relevel(QUD.Graph$Cond, "Instrument-bias Verbs")
QUD.Graph$QCond <- relevel(QUD.Graph$QCond, "Instrument Question")

QUD.Graph2 <- melt(QUD.Graph,
        # ID variables - all the variables to keep but not split apart on
    id.vars=c("TimeFrame","Cond","QCond","Age"),
        # The source columns
    measure.vars=c("Inst.mean","TA.mean", "DA.mean", "DI.mean" ),
        # Name of the destination column that will identify the original
        # column that the measurement came from
    value.name="Prop",
    variable.name ="Quadrant"
    )
QUD.Graph2$Quadrant <- revalue(QUD.Graph2$Quadrant, c("Inst.mean"="Target Instrument", "TA.mean"="Target Animal", "DA.mean" = "Distractor Animal","DI.mean" = "Distractor Instrument"))    
QUD.Graph2$Quadrant <- ordered(QUD.Graph2$Quadrant, levels = c("Target Animal", "Distractor Animal", "Target Instrument", "Distractor Instrument"))
```

And then plot our graphs. The first graph plots mean prop of trials looking at the instrument over the time.

```{r}
ggplot(QUD.Graph,aes(TimeFrame,Inst.mean,linetype = QCond)) + facet_wrap(~Age+Cond) + stat_summary(fun.y = mean, geom = "line", size = 2) + geom_ribbon(aes(ymin=(Inst.mean - Inst.se), ymax=(Inst.mean + Inst.se)), alpha=0.2)+ theme(legend.title=element_blank(),legend.position="bottom")+labs(x = "Time (ms)",y = "Proportion of Looks")
```

The second plot is a standard spaghetti plot, showing looks to each different quadrant.
```{r}
ggplot(QUD.Graph2,aes(TimeFrame,Prop,linetype = Quadrant)) + facet_wrap(~Age+Cond+QCond, nrow = 4, ncol = 2) + stat_summary(fun.y = mean, geom = "line", size = 1) + theme(legend.title=element_blank(),legend.position="bottom")+ theme(legend.title=element_blank(),legend.position="bottom")+scale_linetype_manual(values=c(1,2,3,4))+labs(x = "Time (ms)",y = "Proportion of Looks")
```


To ***analyze*** this data, we split it into two 500ms time windows, beginning 200 and 700ms after the onset of the target word.

```{r}

QUD.Expand$Window <- as.factor(ifelse(QUD.Expand$TimeFrame <700, "EarlyWindow","LateWindow"))
QUD.Window <- summaryBy(Inst~Cond+QCond+Trial+Name.+Age+Window, data = QUD.Expand[QUD.Expand$TimeFrame > 200 & QUD.Expand$TimeFrame < 1200,], FUN = c(mean),keep.names = T,na.rm = T)
QUD.Window$Inst <- ifelse(QUD.Window$Inst > 0,1,0)
contrasts(QUD.Window$QCond)[1] <- -1
contrasts(QUD.Window$Age)[1] <- -1
contrasts(QUD.Window$Cond)[1] <- -1
contrasts(QUD.Window$Window)[1] <- -1
summaryBy(Inst~Age+Window+Cond+QCond, data = QUD.Window)

```

We plot a graph
```{r}
k <- summaryBy(Inst~QCond+Cond+Age+Name.+Window, data = QUD.Window, FUN = c(mean,sd))
k <- summaryBy(Inst.mean~QCond+Cond+Age+Window, data = k, FUN = c(mean,sd))
k$SE = k$Inst.mean.sd/sqrt(6)
tapply(k$Inst.mean.mean, list(k$QCond,k$Window,k$Cond,k$Age), FUN = mean) -> o
tapply(k$SE, list(k$QCond,k$Window,k$Cond,k$Age), FUN = mean) -> se

old.par <- par(mfrow=c(2, 2))
for (i in c(1:2)){
  for (j in c(1:2)){
 barplot(o[,,1,1], beside =T , ylim = c(-0.1,1.1),col = "white",  border = NA, ylab = "Proportion trials gazing at instrument",  names.arg = c("Early Time Window", "Late Time Window"))
 if (i == 1){
 	if (j == 1){
 	 title(main = "5-year-olds hearing \n Equi-biased verbs")
	 legend(1,0.8, legend = c("Instrument Question","Modifier Question"),  bty = "n", col = c("grey","black"), pch = 20)
	 }else{
	 title(main = "5-year-olds hearing \n Instrument-biased verbs")}
	 }else{
	 if (j ==1){
	 title(main = "7-year-olds hearing \n Equi-biased verbs")
	 }else{
	 title(main = "7-year-olds hearing \n Instrument-biased verbs")
	 }
	 }
 points(c(1.8,4.8), o[1,,j,i], pch = 20, cex = 2, col = "black")
 points(c(2.2,5.2), o[2,,j,i], pch = 20, cex = 2, col = "grey",lwd = 2)
 grid(nx = NA, ny = NULL, col = "gray", lty = "dotted",lwd = par("lwd"), equilogs = TRUE)
  arrows(c(1.8,2.2,4.8,5.2), (c(o[,,j,i]) + c(se[,,j,i])+0.01), c(1.8,2.2,4.8,5.2),  (c(o[,,j,i]) - c(se[,,j,i])-0.01), code = 0)
lines(c(1.8,4.8), o[1,,j,i], pch = 15, cex = 5, col = "black", lty = 3)
lines(c(2.2,5.2), o[2,,j,i], pch = 15, cex = 5, col = "black", lty = 3)
}
} 
par(old.par)
```

We run our stats on each time window.

```{r}

# Overall
summary(glmer(Inst~Age*Cond*QCond*Window + (1|Name.) +(0+Window|Name.)+ (1|Trial)+(0+QCond+Window+Age|Trial), data = QUD.Window, family = "binomial",control=glmerControl(optCtrl=list(maxfun=20000), optimizer = "bobyqa" )))

#Stats
#Early window
summary(glmer(Inst~Age*Cond*QCond + (1|Name.) + (1|Trial)+(0+QCond+Age|Trial), data = subset(QUD.Window, Window == "EarlyWindow"), family = "binomial",control=glmerControl(optCtrl=list(maxfun=20000), optimizer = "bobyqa" )))
#Produces interaction btwn age and VerbCond
#Check each age group
summary(glmer(Inst~Cond*QCond + (1|Name.) + (1|Trial)+(0+QCond|Trial), data = subset(QUD.Window, Window == "EarlyWindow" & Age == "5-years"), family = "binomial",control=glmerControl(optCtrl=list(maxfun=20000), optimizer = "bobyqa" )))
summary(glmer(Inst~Cond*QCond + (1|Name.) + (1|Trial)+(0+QCond|Trial), data = subset(QUD.Window, Window == "EarlyWindow" & Age == "7-years"), family = "binomial",control=glmerControl(optCtrl=list(maxfun=20000), optimizer = "bobyqa" )))
#Produces effect of Cond for youngest, and QCond for older.

#Late window
summary(glmer(Inst~Age*Cond*QCond + (1|Name.) + (1|Trial)+(0+QCond+Age|Trial), data = subset(QUD.Window, Window == "LateWindow"), family = "binomial",control=glmerControl(optCtrl=list(maxfun=20000), optimizer = "bobyqa" )))
#Produces interaction btwn age and VerbCond

summary(glmer(Inst~Cond*QCond + (1|Name.) + (1|Trial)+(0+QCond|Trial), data = subset(QUD.Window, Window == "LateWindow" & Age == "5-years"), family = "binomial",control=glmerControl(optCtrl=list(maxfun=20000), optimizer = "bobyqa" )))
summary(glmer(Inst~Cond*QCond + (1|Name.) + (1|Trial)+(0+QCond|Trial), data = subset(QUD.Window, Window == "LateWindow" & Age == "7-years"), family = "binomial",control=glmerControl(optCtrl=list(maxfun=20000), optimizer = "bobyqa" )))
# Youngest show effect of both QCond and Cond
# Oldest only show effect of QCond
```
